\thetitle

### 2021-03-08 writing/mutate-interesting.tex
Add explanation to interesting mutant breakdown figure (6)

\begin{figure*} \footnotesize
 \centering
 \includegraphics[scale=0.33]{./plots/mutant-breakdown}
  Counts are cut off at 50.

\caption{The generated debugging scenarios across all benchmarks} 
 \label{fig:mutant-breakdown}
\end{figure*}

>>>>

\begin{figure}
 \centering
 \includegraphics[scale=0.33]{./plots/mutant-breakdown}

 \vspace{1em}

 \begin{minipage}{\textwidth}
 Each plot shows a breakdown of interesting mutants by mutator.
 Each mutator corresponds to a bar representing the number of interesting mutants generated by that mutator.
 The counts are cut off at 50, so those bars reaching the edge of the plot represent 50 or more interesting mutants.
 \end{minipage}

\caption{Breakdown of interesting mutants by mutator, per benchmark.}
 \label{fig:mutant-breakdown}
\end{figure}
